Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-04-26 paper/document.tex
Updates.

\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\centering
\caption{Summary of projects used in the evaluation.}
\label{tab:project-summary}
\begin{tabular}{c|lllll}
\hline
\bfseries Project & \bfseries Commits & \bfseries Authors* & \bfseries Files &   \bfseries Types &  \bfseries  Changes\\
\hline
ANTLR4 & 3930 & 27 & 1793 & 2635 & 58425\\
BookKeeper & 660 & 12 & 758 & 1872 & 31817\\
Curator & 1524 & 43 & 1211 & 1269 & 27957\\
Tika & 860 & 10 & 604 & 757 & 20764\\
\hline
\multicolumn{6}{p{\linewidth}}{\footnotesize Totals for the four projects we analyzed. ``Changes'' refers to the total number of invocation or declaration changes observed from the AST. Note that the number given for authors may be larger than the actual number of collaborators on the project, due to some collaborators using multiple email address, and thus appearing as more than one author.}
\end{tabular}
\end{table}

@@

Bug triaging for large open source projects is a very time consuming task \cite{badashian2015}, with hundreds  of bugs being reported daily. Each bug must be processed and assigned to a developer that has the experience required to fix the bug. In order to be effective, the triager has to have knowledge of what each developer has worked on as well as the parts of the code may be affected by the bugs. Being able to directly see what types a developer has worked with over time is important information for triaging. If the type causing the bug is known, the developers which have recently used that type can be assigned the bug. The commit messages for the affected types are also visible, providing greater context about how the type has been used. The developer who is assigned the bug can also use type information to locate other affected pieces of code and know which developers have been using the affected types.

>>>>

\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\centering
\caption{Summary of projects used in the evaluation.}
\label{tab:project-summary}
\begin{tabular}{c|ccccc}
\hline
\bfseries Project & \bfseries Commits & \bfseries Authors & \bfseries Files &   \bfseries Types &  \bfseries  Changes\\
\hline
ANTLR4 & 3930 & 27 & 1793 & 2635 & 58425\\
BookKeeper & 660 & 12 & 758 & 1872 & 31817\\
Curator & 1524 & 43 & 1211 & 1269 & 27957\\
Tika & 860 & 10 & 604 & 757 & 20764\\
\hline
\multicolumn{6}{p{3.25in}}{\footnotesize Totals for the four projects we analyzed. ``Changes'' refers to the total number of invocation or declaration changes observed from the AST diffs. Note that the number given for authors may be larger than the actual number of collaborators on the project, due to some collaborators using multiple email address, thus appearing as more than one author.}
\end{tabular}
\end{table}

@@

Bug triaging for large open source projects is a very time consuming task \cite{badashian2015}, with hundreds  of bugs being reported daily. Each bug must be processed and assigned to a developer that has the experience required to fix the bug. In order to be effective, the triager has to have knowledge of what each developer has worked on as well as the parts of the code may be affected by the bugs. With TypeV, the triager is able to directly see what types a developer has worked with over time. This is important information for triaging since the type causing the bug, if known, will have a list of associated developers who have recently used that type and can be assigned the bug. The commit messages for the affected types are also visible, providing greater context about how the type has been used. The assigned developer can also use type information to locate other pieces of code affected by a bug and know which developers have been using the affected types.
